Silent pessimists: researchers' perceptions of malaria eradication

### 2018-01-02 paper.Rmd
fixed heckman errors

```{r}
# Estimate model for de-biasing sample selection without Heckman.
response_model <- glm(responded ~ bin_citations + sex, data = df, family = binomial('logit'))
# Use model to predict likelihood of response
df$likelihood_of_response <- predict(response_model, df, type = 'response')
# Use inverse of likelihood of response to assign weight for model
df$weight <- 1 - df$likelihood_of_response
# Run likelihood of eradication models
for (i in seq(10, 50, 10)){
  assign(paste0('formula_simple_years_', i),
         as.formula(paste0('years_',
                           i,
                           '_numeric ~ sex + bin_citations')))
  assign(paste0('simple_', i),
         lm(get(paste0('formula_simple_years_', i)), data = df))
  assign(paste0('simple_', i, '_weighted'),
         lm(get(paste0('formula_simple_years_', i)), data = df,
            weights = df$weight))

@@

# Get aggregate adjusted vs unadjusted likelihoods of eradications
simple <- data_frame(years = seq(10, 50, 10),
                     adjusted = NA,
                     unadjusted = NA)
for (i in seq(10, 50, 10)){
   simple$unadjusted[simple$years == i] <- mean(df[,paste0('years_', i, '_numeric')], na.rm = TRUE)
   simple$adjusted[simple$years == i] <- weighted.mean(x = df[,paste0('years_', i, '_numeric')],
                                                       w = ifelse(is.na(df$weight), 0,
                                                                  df$weight), na.rm = TRUE)
  # simple_model <- get(paste0('simple_', i))
  # weighted_model <- get(paste0('simple_', i, '_weighted'))

}
simple <- gather(simple, key, value, adjusted:unadjusted)
g2 <- ggplot(data = simple,
       aes(x = years,
           y = value,
           color = key,
           lty = key)) +
    geom_line(alpha = 0.8) +
  geom_point(alpha = 0.6) +
  theme_paper() +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'B: Perceived likelihood of eradication: Adjusted and unadjusted') +
  scale_linetype_manual(name = '', values = 1:2) +
  scale_color_manual(name = '', values = c('blue', 'darkorange'))
x <- df %>%
  group_by(citations = bin_citations) %>%
  summarise(years_10 = mean(years_10_numeric, na.rm = TRUE),
            years_20 = mean(years_20_numeric, na.rm = TRUE),
            years_30 = mean(years_30_numeric, na.rm = TRUE),
            years_40 = mean(years_40_numeric, na.rm = TRUE),
            years_50 = mean(years_50_numeric, na.rm = TRUE),
            n = length(unique(email))) %>%
  ungroup %>%
  gather(key, value, years_10:years_50) %>%
  filter(!is.na(citations))

cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
                         )(length(unique(x$citations)))
g1 <- ggplot(data = x %>% filter(!is.na(citations)),
       aes(x = as.numeric(gsub('years_', '', key)),
           y = value,
           color = citations,
           group = citations)) +
  geom_point(alpha = 0.7) +
  geom_line(alpha = 0.6) +
  theme_paper() +
  scale_color_manual(name = 'Number of citations',
                     values = cols) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
```

@@

\vfill\null
\columnbreak

@@

cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
                         )(length(unique(x$citations)))
x1 <- ggplot(data = x %>% filter(!is.na(citations)),
       aes(x = as.numeric(gsub('years_', '', key)),
           y = value,
           color = citations,
           group = citations)) +
  geom_point(alpha = 0.7) +
  geom_line(alpha = 0.6) +
  theme_paper() +
  scale_color_manual(name = 'Number of citations',
                     values = cols) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'A: Difference in perceived likelihood of eradication by citations')

x2 <- 
  ggplot(data = heckman,
       aes(x = years,
           y = value,
           color = key,
           lty = key)) +
  geom_line(alpha = 0.8) +
  geom_point(alpha = 0.6) +
  theme_paper() +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'B: Perceived likelihood of eradication: Heckman method and unadjusted') +
  scale_linetype_manual(name = '', values = 1:2) +
  scale_color_manual(name = '', values = c('blue', 'darkorange'))
```

>>>>

```{r}
# Estimate model for de-biasing sample selection without Heckman.
response_model <- glm(responded ~ bin_citations + sex, data = df, family = binomial('logit'))
# Use model to predict likelihood of response
df$likelihood_of_response <- predict(response_model, df, type = 'response')
# Use inverse of likelihood of response to assign weight for model
df$weight <- 1 - df$likelihood_of_response
# Run likelihood of eradication models
for (i in seq(10, 50, 10)){
  assign(paste0('formula_simple_years_', i),
         as.formula(paste0('years_',
                           i,
                           '_numeric ~ sex')))

                           # '_numeric ~ sex + bin_citations')))
  # assign(paste0('simple_', i),
  #        lm(get(paste0('formula_simple_years_', i)), data = df))
  assign(paste0('simple_', i, '_weighted'),
         lm(get(paste0('formula_simple_years_', i)), data = df,
            weights = df$weight))

@@

# Get aggregate adjusted vs unadjusted likelihoods of eradications
simple <- data_frame(years = seq(10, 50, 10),
                     adjusted = NA,
                     unadjusted = NA)
simple$unadjusted <- heckman$value[heckman$key == 'Unadjusted']
for (i in seq(10, 50, 10)){
   # simple$unadjusted[simple$years == i] <- mean(df[,paste0('years_', i, '_numeric')], na.rm = TRUE)
   simple$adjusted[simple$years == i] <- weighted.mean(x = df[,paste0('years_', i, '_numeric')],
                                                       w = ifelse(is.na(df$weight), 0,
                                                                  df$weight), na.rm = TRUE)
  # simple_model <- get(paste0('simple_', i))
  # weighted_model <- get(paste0('simple_', i, '_weighted'))

}
simple <- gather(simple, key, value, adjusted:unadjusted)
g2 <- ggplot(data = simple,
       aes(x = years,
           y = value,
           color = key,
           lty = key)) +
    geom_line(alpha = 0.8) +
  geom_point(alpha = 0.6) +
  theme_paper(base_size = 13) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'B: Perceived likelihood of eradication: Adjusted and unadjusted') +
  scale_linetype_manual(name = '', values = 1:2) +
  scale_color_manual(name = '', values = c('blue', 'darkorange'))
x <- df %>%
  group_by(citations = bin_citations) %>%
  summarise(years_10 = mean(years_10_numeric, na.rm = TRUE),
            years_20 = mean(years_20_numeric, na.rm = TRUE),
            years_30 = mean(years_30_numeric, na.rm = TRUE),
            years_40 = mean(years_40_numeric, na.rm = TRUE),
            years_50 = mean(years_50_numeric, na.rm = TRUE),
            n = length(unique(email))) %>%
  ungroup %>%
  gather(key, value, years_10:years_50) %>%
  filter(!is.na(citations))

cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
                         )(length(unique(x$citations)))
g1 <- ggplot(data = x %>% filter(!is.na(citations)),
       aes(x = as.numeric(gsub('years_', '', key)),
           y = value,
           color = citations,
           group = citations)) +
  geom_point(alpha = 0.7) +
  geom_line(alpha = 0.6) +
  theme_paper(base_size = 13) +
  scale_color_manual(name = 'Number of citations',
                     values = cols) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'A: Difference in perceived likelihood of eradication by citations')
```

\vfill\null

@@

\columnbreak

@@

cols <- colorRampPalette(c('red', 'orange', 'blue') #brewer.pal(n = 9, 'Spectral')
                         )(length(unique(x$citations)))
x1 <- ggplot(data = x %>% filter(!is.na(citations)),
       aes(x = as.numeric(gsub('years_', '', key)),
           y = value,
           color = citations,
           group = citations)) +
  geom_point(alpha = 0.7) +
  geom_line(alpha = 0.6) +
  theme_paper(base_size = 13) +
  scale_color_manual(name = 'Number of citations',
                     values = cols) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'A: Difference in perceived likelihood of eradication by citations')

x2 <- 
  ggplot(data = heckman,
       aes(x = years,
           y = value,
           color = key,
           lty = key)) +
  geom_line(alpha = 0.8) +
  geom_point(alpha = 0.6) +
  theme_paper(base_size = 13) +
  labs(x = 'Years',
       y = 'Likelihood of eradication',
       subtitle = 'B: Perceived likelihood of eradication: Heckman method and unadjusted') +
  scale_linetype_manual(name = '', values = 1:2) +
  scale_color_manual(name = '', values = c('blue', 'darkorange'))
```

\vfill\null
